\section{Future Work}
Given the deadline for the project, there are always things that could have been included, had there been more time. Below is a list of the things the group would like to work on:

For the NXT application:
\begin{itemize}
	\item Optimize the NXT application to aim horizontally and vertically at the same time, thus minimizing the time it takes to aim.
	\item Allow automatic restart. This will work well if the turret is modified to either be able to fire multiple projectiles or automatically reload.
	\item Add math to predict movement of accelerating targets and targets moving in half circles.
\end{itemize}

For Kinect:
\begin{itemize}
	\item Better image analysis might eliminate some of the noise in the target detection. Depending on how it is done, this could potentially make the sensor slow, and will have to be implemented carefully.
	\item Better sorting of data out of normal range, i.e. automatic sorting of unusable results. 
\end{itemize}

Turret design:
\begin{itemize}
	\item Fixate the Kinect on the turret to improve precision. Currently the Kinect has to be adjusted every time the turret is moved, and if they are not aligned properly the precision suffers greatly.
	\item More focus on stability. Currently the turret is compact, which is good, but it could be improved to be even less wobbly when aiming, allowing the motors to operate at higher speeds.
	\item The design should be altered to allow more movement in an even wider angle than is possible at the moment. 
\end{itemize}